Generalized Plackett-Luce Likelihoods

### 2023-07-24 inst/jss_4832_minorcomments_rebuttal.tex

\documentclass[12pt]{article}
\usepackage{xcolor}
\begin{document}

\section*{JSS4832: Generalized Plackett-Luce Likelihoods by Robin
K. S. Hankin}

Below, the reviewer's comments are in black, and the replies to the
issues are in \textcolor{blue}{blue}.  I have indicated changes to
the manuscript where appropriate.

\textcolor{blue}{Short story: I have accommodated all the comments with
rewording and clarification.}

From the editorial team:

I had a closer look at the revision of 4832 and, as far as I'm
concerned, the paper can be accepted as it is. However, I wanted to
draw your attention to the author's rebuttal file, p.7. It seems that
he doesn't agree that this paper should be published as code snippet,
as opposed to a regular paper. I'm not sure whether this was
previously communicated to the author by the editorial team. Anyway, I
think it would be good if the editorial team could clarify this issue
directly with the author.

\textcolor{blue}{Happy to classify as a code snippet if the editors
  wish, although I stand by my previous comments.  Happy either way.}

Also, I think he misunderstood my concerns about the supplemental R
code file (see bottom of p.7 in the rebuttal file). What I'm asking
for is to make the R code look nicer with proper comments, as opposed
to just pull it from the Rnw file. In addition, the code starts with

\begin{verbatim}
source("loadlibrary.R",echo=FALSE) # to avoid stupid messages
opts_chunk$set(cache=TRUE, autodep=TRUE)
\end{verbatim}

This is not reproducible. Also, the author doesn't even load the hyper2 package.

\textcolor{blue}{Fixed, code fully reproducible}

So, while I think the paper is in good shape, the code file is not. But this can be easily be fixed.

Manuscript style comments:

\begin{itemize}
  \item Please use "R>" as the command prompt, rather than ">".
\end{itemize}

\textcolor{blue}{fixed}

\begin{itemize}
\item The code presented in the manuscript should not contain comments
within the verbatim code. Instead the comments should be made in the
normal LaTeX text.
\end{itemize}

\textcolor{blue}{fixed}

\begin{itemize}
  \item For the code layout in R publications, we typically distinguish
input/output using Sinput/Soutput (or equivalently
CodeInput/CodeOutput). Unless there are special reasons to format it
differently, the input should use the text width (up to 76 or 77
characters) and be indented by two spaces, e.g.,

\begin{verbatim}
\begin{Sinput}
R> example_model <- lm(response ~ variable1 + variable2 + variable3,

weights = w, data = mydata)
\end{Sinput}
\end{verbatim}
\end{itemize}

\textcolor{blue}{fixed}

 As a reminder, please make sure that: \proglang, \pkg and \code have
 been used for highlighting throughout the paper (including titles and
 references), except where explicitly escaped.

\textcolor{blue}{fixed}

References:

\begin{itemize}
      \item MATLAB (not: Matlab, matlab)
guages. Hunter (2004), for example, presents results in matlab [although he works with a
\end{itemize}
\textcolor{blue}{fixed}

\begin{itemize}
\item As a reminder,
- Please make sure that all software packages are \cite{}'d properly.

- All references should be in title style.

- See FAQ for specific reference instructions.
Code:
\end{itemize}

\begin{itemize}
\item As a reminder, please make sure that the files needed to replicate
all code/examples within the manuscript are included in a standalone
replication script.
\end{itemize}
\textcolor{blue}{fixed}

\end{document}

### 2023-08-23 inst/jss_4832_minorcomments_rebuttal.tex

\documentclass[12pt]{article}
\usepackage{xcolor}
\begin{document}

\section*{JSS4832: Generalized Plackett-Luce Likelihoods by Robin
K. S. Hankin}

Below, the reviewer's comments are in black, and the replies to the
issues are in \textcolor{blue}{blue}.  I have indicated changes to
the manuscript where appropriate.

\textcolor{blue}{Short story: I have accommodated all the comments and
  in particular have refactored the replication script as requested.}

@@

\textcolor{blue}{Fixed, code fully reproducible}

So, while I think the paper is in good shape, the code file is not. But this can be easily be fixed.

Manuscript style comments:

\begin{itemize}
  \item Please use \verb+"R>"+ as the command prompt, rather than \verb+">"+.
\end{itemize}

@@

\begin{verbatim}
\begin{Sinput}
R> example_model <- lm(response ~ variable1 + variable2 + variable3,

weights = w, data = mydata)
\end{Sinput}
\end{verbatim}
\end{itemize}

\textcolor{blue}{fixed}

\begin{itemize}
  \item
 As a reminder, please make sure that: \verb+\proglang+, \verb+\pkg+
 and \verb+\code+ have been used for highlighting throughout the paper
 (including titles and references), except where explicitly escaped.
\end{itemize}
\textcolor{blue}{fixed}

\begin{itemize}
      \item MATLAB (not: Matlab, matlab)
guages. Hunter (2004), for example, presents results in matlab [although he works with a
\end{itemize}

@@

\begin{itemize}
      \item MATLAB (not: Matlab, matlab)
guages. Hunter (2004), for example, presents results in matlab [although he works with a
\end{itemize}

\textcolor{blue}{fixed}

\begin{itemize}
\item As a reminder,
- Please make sure that all software packages are \verb+\cite{}+'d properly.

### 2023-08-23 inst/jss_hyper3.Rnw
minor changes

<<setup, cache=FALSE,echo=FALSE>>=
source("loadlibrary.R",echo=FALSE)  # to avoid stupid messages 
opts_chunk$set(cache=TRUE, autodep=TRUE)
@

@@

Computational support for Bradley-Terry likelihood functions is
available in a range of languages.  \cite{hunter2004}, for example,
presents results in \proglang{matlab} [although he works with a
nonlinear extension to account for ties]; \cite{allison1994} present
related work for ranking statistics in \proglang{SAS} and
\cite{maystre2022} has released a \proglang{python} package for
Luce-type choice datasets.

@@

\begin{verbatim}
weightedplayervector n,d;
n["a"] = 1; // n for numerator
d["a"] = 3; // d for denominator
d["b"] = 2;
d["c"] = 1;

@@

Above, object \code{L} is an object of class \code{hyper3}; it may be
evaluated at points in probability space [that is, a vector
\code{[a,b,c]} of nonnegative values with unit sum] using standard
\proglang{R} idiom wrapping \proglang{C++} back end.

>>>>

<<setup, cache=FALSE,echo=FALSE>>=
source("loadlibrary.R",echo=FALSE)  # to avoid stupid messages 
opts_chunk$set(cache=TRUE, autodep=TRUE)
options(prompt = "R> ")
@

@@

Computational support for Bradley-Terry likelihood functions is
available in a range of languages.  \cite{hunter2004}, for example,
presents results in \proglang{MATLAB} [although he works with a
nonlinear extension to account for ties]; \cite{allison1994} present
related work for ranking statistics in \proglang{SAS} and
\cite{maystre2022} has released a \proglang{python} package for
Luce-type choice datasets.

@@

\begin{verbatim}
weightedplayervector n,d;
n["a"] = 1; 
d["a"] = 3; 
d["b"] = 2;
d["c"] = 1;

@@

Above, we understand \code{n} and \code{d} to represent numerator and
denominator respectively.  Object \code{L} is an object of class
\code{hyper3}; it may be evaluated at points in probability space
[that is, a vector \code{[a,b,c]} of nonnegative values with unit sum]
using standard \proglang{R} idiom wrapping \proglang{C++} back end.
